Utilizing Convolution for Obstacle Avoidance during Robotic Manipulator Movement

### 2023-07-27 Articles/ERK/erk.tex
.

Despite its effectiveness, the approach could potentially fall into local minima traps. This limitation could be addressed by incorporating multiple convolutional kernels, though this would increase complexity and resemble a structure of a convolutional neural networks.

>>>>

Despite its effectiveness, the approach could potentially fall into local minima traps. This limitation could be addressed by incorporating multiple convolutional kernels, though this would increase complexity and resemble a structure of convolutional neural networks.
